#Packages used to create the projections

library(tidyverse) 
library(rvest)

# these are all the funtions you will need to use to create the projections. 

# function 1: Use this function to get the seasons required for the Marcel projections

```{r function}

get_hockeyref <- function(url){

# Read in HTML
  
read_url <- read_html(url)
  
# select the table on hockey ref

url_table <- read_url %>% html_nodes("table") %>% html_table()

url_table_unlist <- url_table[[1]] 

# create headings for your table

headings <- c("Rk", "Player", "Age", "Team", "Pos", "GP", "G", "A", 
              "P","P.M", "PIM","PS","EVG", "PPG", "SHG", "GWG",
              "EVA","PPA","SHA", "SOG", "SH.p", "TOI", "TOI.GP",
              "BLK","HIT", "FOW", "FOL", "FO.P"
              )

# insert headings into appropriate columns

colnames(url_table_unlist) <- headings

# remove headings that were put into 1st row

url_table_unlist2 <- url_table_unlist[-1,]

# convert character strings to numeric

num_table <-  url_table_unlist2 %>% 
              mutate_at(vars("Age", "GP", "G", "A", "P", "P.M",
                             "PIM","PS","EVG","PPG", "SHG", "GWG",
                             "EVA", "PPA","SHA", "SOG", "SH.p",
                             "TOI","BLK","HIT", "FOW", "FOL", "FO.P"),
                        as.numeric) 

# remove NAs & convert to 0 & remove special characters like *

num_table2 <-  num_table[!is.na(num_table$GP), ] %>% 
               mutate_all(~replace(., is.na(.), 0))

num_table2 <- num_table2 %>% mutate(Player = gsub("\\*", "", Player))

# convert TOI to numeric version

num_table2 <- num_table2 %>% mutate(TOI.GP = round(TOI/GP,2))

# remove duplicate names, keep only TOT if duplicate names present

filtered_table <- num_table2 %>%
                  distinct(Rk, .keep_all = TRUE)
                  
filtered_table                  

}
```

# function 2: use this function to get the information we want from the scrapped tables

```{r function}

get_info <- function(season){

info <- season %>% transmute(
                      season = season,
                      player = Player,
                      age = Age,
                      team = Team, 
                      pos = if_else(Pos != "D", "F", "D"),
                      gp = GP,
                      toi.gp = TOI.GP,
                      tot.toi = gp*toi.gp,
                      g = G,
                      a = A,
                      p = P,
                      ppg = PPG,
                      ppa = PPA,
                      shg = SHG,
                      sha = SHA,
                      sog = SOG,
                      blk = BLK,
                      hit = HIT,
                      pim = PIM,
                      fow = FOW,
                      fol = FOL,
                      playerID = PlayerID,
                      weight = weight
)

info

}
```

# function 3: use this function to create league averages for each position

``` {r function}

season_average <- function(season){

lg_avg_season <- season %>%
          # ensure that only regulars impact the averages 
          filter(gp >= max(.25*gp)) %>%
          # we need to have averages for forwards and defenceman
          group_by(pos) %>%
          summarize(
          lg_avg_gp = mean(gp, na.rm = TRUE),
          lg_avg_toi_gp = mean(toi.gp, na.rm = TRUE),
          lg_avg_toi = mean(tot.toi, na.rm = TRUE),
        lg_avg_g = mean(g, na.rm = TRUE),
        lg_avg_a = mean(a, na.rm = TRUE),
        lg_avg_pts = mean(p, na.rm = TRUE),
        lg_avg_ppg = mean(ppg, na.rm = TRUE),
        lg_avg_ppa = mean(ppa, na.rm = TRUE),
        lg_avg_shg = mean(shg, na.rm = TRUE),
        lg_avg_sha = mean(sha, na.rm = TRUE),
        lg_avg_sog = mean(sog, na.rm = TRUE),
        lg_avg_blk = mean(blk, na.rm = TRUE),
        lg_avg_hit = mean(hit, na.rm = TRUE),
        lg_avg_pim = mean(pim, na.rm = TRUE),
        lg_avg_fow = mean(fow, na.rm = TRUE),
        lg_avg_fol = mean(fol, na.rm = TRUE)
                )
         
lg_avg_season
}

```

# function 4. This uses the previous 3 functions to create the projections

```{r function}

proj_season <- function(year){

season <- year
  
# you will need 3 seasons worth of data. 

n1 <- season - 1
n2 <- season - 2
n3 <- season - 3

# This will act as our LCV

seasons <- c(n1,n2,n3)

# Using a for loop we can get the 3 seasons directly from HockeyRef

# j acts as our identifier for DF
j <- 1
# creates 1xL vector of lists
df_season <- vector("list",length(seasons))
for(i in seasons){
#create our url for hockeyref scraping
url <- paste0("https://www.hockey-reference.com/leagues/NHL_", i,"_skaters.html")
# call our scraper function and error catch function
df_season[[j]] <- tryCatch(get_hockeyref(url),
                  error = function(e) NULL)
print(j)
j<-j+1
Sys.sleep(0.5)
}

# turn each list into it's own season

n1_season <- bind_rows(df_season[1])
n2_season <- bind_rows(df_season[2])
n3_season <- bind_rows(df_season[3])

# Add a season. Where n1 is the season before the proj season and so on. Eg: If projecting 2023 the n1 season is 2022

n1_season$season <- "n1"
n2_season$season <- "n2"
n3_season$season <- "n3"

# Add the weights we will be using for the weighted average

n1_season$weight <- 6
n2_season$weight <- 3
n3_season$weight <- 1

# Create playerID for duplicate names. Eg: There are 2 Sebastian Aho's in the 2023 projection

n1_season$PlayerID <- paste(gsub(" ", "", n1_season$Player),n1_season$Age+1, sep ="")

n2_season$PlayerID <- paste(gsub(" ", "", n2_season$Player),n2_season$Age+2, sep ="")

n3_season$PlayerID <- paste(gsub(" ", "", n3_season$Player),n3_season$Age+3, sep ="")

# create the transformed versions of each season. Filter out anyone that has < 9 GP

season_n1 <- get_info(n1_season) %>% filter(gp > 10)
season_n2 <- get_info(n2_season) %>% filter(gp > 10)
season_n3 <- get_info(n3_season) %>% filter(gp > 10)

# Call the league average function and create averages for each of the seasons

n1_average <- season_average(season_n1)
n2_average <- season_average(season_n2)
n3_average <- season_average(season_n3)

# Add the appropriate seasonal tag

n1_average$season <- "n1"
n2_average$season <- "n2"
n3_average$season <- "n3"

# join the league avg and player seasons

n1_joined <- merge(season_n1,n1_average, by = c("season", "pos"))
n2_joined <- merge(season_n2,n2_average, by = c("season", "pos"))
n3_joined <- merge(season_n3,n3_average, by = c("season", "pos"))

# create the weighted values for each season. Do this using mutate_at

weight_n1 <- n1_joined %>% mutate_at(vars(c(
                      "tot.toi", "g", "a", "p", "ppg",
                      "ppa","shg","sha", "sog", "blk", "hit",
                      "pim", "fow","fol","lg_avg_toi","lg_avg_pts",
                      "lg_avg_g", "lg_avg_a","lg_avg_ppg",
                      "lg_avg_ppa","lg_avg_shg","lg_avg_sha",
                      "lg_avg_sog","lg_avg_blk","lg_avg_hit",
                      "lg_avg_pim","lg_avg_fow","lg_avg_fol"
                      )), ~.*weight)
                      
weight_n2 <- n2_joined %>% mutate_at(vars(c(
                      "tot.toi", "g", "a", "p", "ppg",
                      "ppa","shg","sha", "sog", "blk", "hit",
                      "pim", "fow","fol","lg_avg_toi","lg_avg_pts",
                      "lg_avg_g", "lg_avg_a","lg_avg_ppg",
                      "lg_avg_ppa","lg_avg_shg","lg_avg_sha",
                      "lg_avg_sog","lg_avg_blk","lg_avg_hit",
                      "lg_avg_pim","lg_avg_fow","lg_avg_fol"
                      )), ~.*weight)     
                      
weight_n3 <- n3_joined %>% mutate_at(vars(c(
                      "tot.toi", "g", "a", "p", "ppg",
                      "ppa","shg","sha", "sog", "blk", "hit",
                      "pim", "fow","fol","lg_avg_toi","lg_avg_pts",
                      "lg_avg_g", "lg_avg_a","lg_avg_ppg",
                      "lg_avg_ppa","lg_avg_shg","lg_avg_sha",
                      "lg_avg_sog","lg_avg_blk","lg_avg_hit",
                      "lg_avg_pim","lg_avg_fow","lg_avg_fol"
                      )), ~.*weight)                      

# combine the seasons using playerID as the join. We will also filter out anyone that played less than 9 games in either season. We will also create the proj_toi stat

joined_seasons <- merge(merge(weight_n1,
                  weight_n2,by ="playerID", all = TRUE),weight_n3, 
                  by = "playerID", all = TRUE) %>% 
      # filter out anyone that hasn't played in n1 or n2 seasons
                  filter(gp.x > 9 | gp.y > 9) %>%
      # create proj_toi based on which season(s) a player played in
                  mutate(proj_toi = case_when(
        (pos.x == "F" & season.y == "n2" & season.x == "n1") ~ 
        0.10 * toi.gp.y+0.80 * toi.gp.x + 1.5,
        (pos.x == "F" & is.na(season.y) & season.x == "n1") ~ 
        0.80 * toi.gp.x + 3,
        (pos.y == "F" & is.na(season.x) & season.y == "n2") ~ 
        0.80 * toi.gp.y + 2.5,
        (pos.x == "D" & season.y == "n2" & season.x == "n1") ~ 
        0.20 * toi.gp.y+0.70 * toi.gp.x + 2,
        (pos.x == "D" & is.na(season.y) & season.x == "n1") ~ 
        0.8 * toi.gp.x + 4,
        (pos.y == "D" & is.na(season.x) & season.y == "n2") ~ 
        0.8 * toi.gp.y + 3.5,
        TRUE ~ 0.00)) %>%
                #Update age to proj season age
                 mutate(new_age = case_when(
                 is.na(age.x) ~ age.y+2,
                 is.na(age.x) & is.na(age.y) ~ age+3,
                 !is.na(age.x) ~ age.x+1),
                 new_pos = case_when(
                 is.na(pos.x) ~ pos.y,
                 is.na(pos.x) & is.na(pos.y) ~ pos,
                 !is.na(pos.x) ~ pos.x)
                 ) %>% 
                 # replace all NAs with 0s
                 mutate_all(~replace(., is.na(.), 0))
                 
                 
# Easiest way to get the max number of gp is to find the mode. Use this function

get_mode <- function(vector) {
   uniq_number <- unique(vector)
   uniq_number[which.max(tabulate(match(vector, uniq_number)))]
}

# define the mode for each season

n1_gp_mode <- get_mode(season_n1$gp)

n2_gp_mode <- get_mode(season_n2$gp)

# Using case_when create GP projections based on specific conditions, 22 cases in all. 
# depth F is if toi <= 12, depth D is if toi <= 17.50
# Also  add  3 of seasons together to create single weighted value for each stat

sum_plyr <- joined_seasons %>%
                transmute(
                playerID = playerID,
                player = ifelse(player.x == 0,player.y, player.x),
                age = new_age,
                pos = new_pos,
                gp = case_when(
            #1. GP proj for depth F, 2 seasons
                gp.x <= 0.4*n1_gp_mode & gp.y <= 0.4*n2_gp_mode & pos == "F"
                & proj_toi <= 14 ~
                round(40*.6+.2*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)
                +.2*if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y)*82)),
            #2. GP proj for depth D, 2 seasons
                gp.x <= 0.4*n1_gp_mode & gp.y <= 0.4*n2_gp_mode & pos == "D" 
                & proj_toi <= 17.5 ~
                round(40*.6+.2*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)
                +.2*if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y)*82)),
            #3. GP proj for F, 2 seasons > 41
                gp.x > 0.4*n1_gp_mode & gp.y > 0.4*n2_gp_mode & pos == "F"~
                round(76*.5+.25*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)
                +.25*if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y)*82)),
            #4. GP proj for D, 2 seasons > 41
                gp.x > 0.4*n1_gp_mode & gp.y > 0.4*n2_gp_mode & pos == "D"~
                round(76*.5+.25*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82) 
                +.25*if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y)*82)),
            #5. GP proj for rookie non depth F, n1 season > 41
                gp.x > 0.4*n1_gp_mode & gp.y == 0 & pos == "F" ~
                round(74*.7+.3*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)),
            #6. GP proj for rookie depth D,  n1 season > 41
                gp.x > 0.4*n1_gp_mode & gp.y == 0 & pos == "D" ~
                round(74*.7+.3*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)),
            #7. GP proj for non depth F, n1 szn < 41, n2 szn > 41
                gp.x <= 0.4*n1_gp_mode & gp.y > 0.4*n2_gp_mode & pos == "F" 
                & proj_toi > 14.0 ~
                round(74*.6+.15*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)
                +.25*if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y)*82)),
            #8. GP proj for non depth D, n1 szn < 41, n2 szn > 41
                gp.x <= 0.4*n1_gp_mode & gp.y > 0.4*n2_gp_mode & pos == "D"
                & proj_toi > 17.5 ~
                round(74*.6+.15*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)
                +.25*if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y)*82)),
            #9. GP proj for non depth F, n1 szn > 41, n2 szn < 41
                gp.x > 0.4*n1_gp_mode & gp.y <= 0.4*n2_gp_mode & pos == "F"
                & proj_toi > 14.0 ~
                round(74*.6+.25*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)
                +.15*if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y)*82)),
            #10.GP proj for non depth D, n1 szn > 41, n2 szn < 41
                gp.x > 0.4*n1_gp_mode & gp.y <= 0.4*n2_gp_mode & pos == "D"
                & proj_toi > 17.5~
                round(74*.6+.25*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)
                +.15*if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y)*82)),
            #11.GP proj for non depth F, 2 seasons 
                gp.x <= 0.4*n1_gp_mode & gp.y <= 0.4*n2_gp_mode & pos == "F" 
                & proj_toi > 14.0 ~
                round(74*.8+.10*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)
                +.10*if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y)*82)),
            #12.GP proj for non depth D, 2 seasons
                gp.x <= 0.4*n1_gp_mode & gp.y <= 0.4*n2_gp_mode & pos == "D" 
                & proj_toi > 17.5 ~
                round(74*.8+.10*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)
                +.10*if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y)*82)),
            #13.GP proj for depth F, n1 szn < 41, n2 szn > 41
                gp.x <= 0.4*n1_gp_mode & gp.y > 0.4*n2_gp_mode & pos == "F" 
                & proj_toi <= 14.0 ~
                round(40*.7+.125*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)
                +.175*if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y)*82)),
            #14.GP proj for depth D, n1 szn < 41, n2 szn > 41
                gp.x <= 0.4*n1_gp_mode & gp.y > 0.4*n2_gp_mode & pos == "D"
                & proj_toi <= 17.5 ~
                round(40*.7+.125*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)
                +.175*if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y))*82),
            #15.GP proj for depth F, n1 szn > 41, n2 szn < 41
                gp.x > 0.4*n1_gp_mode & gp.y <= 0.4*n2_gp_mode & pos == "F"
                & proj_toi <= 14.0 ~
                round(40*.7+.175*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)
                +.125**if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y)*82)),
            #16.GP proj for depth D, n1 szn > 41, n2 szn < 41
                gp.x > 0.4*n1_gp_mode & gp.y <= 0.4*n2_gp_mode & pos == "D"
                & proj_toi <= 17.5~
                round(40*.7+.175*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)
                +.125*if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y))*82),
            #17.GP proj for depth F, n1 szn < 41, n2 szn > 41
                gp.x <= 0.4*n1_gp_mode & gp.y > 0.4*n2_gp_mode & pos =="F" 
                & proj_toi <= 14.0 ~
                round(40*.7+.125*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)
                +.175*if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y)*82)),
            #18.GP proj for depth D, n1 szn < 41, n2 szn > 41
                gp.x <= 0.4*n1_gp_mode & gp.y > 0.4*n2_gp_mode & pos =="D"
                & proj_toi <= 17.5 ~
                round(40*.7+.125*if_else((gp.x/max(gp.x)*82) >= 82, 82,gp.x/max(gp.x)*82)
                +.175*if_else((gp.y/max(gp.y)*82) >= 82, 82,gp.y/max(gp.y)*82))
           ),
                  proj_toi = round(proj_toi,2),
                  sum_g = g.x+g.y+g,
                  sum_a = a.x+a.y+a,
                  sum_p = p.x+p.y+p,
                  sum_ppg = ppg.x+ppg.y+ppg,
                  sum_ppa = ppa.x+ppa.y+ppa,
                  sum_shg = shg.x+shg.y+shg,
                  sum_sha = sha.x+sha.y+sha,
                  sum_sog = sog.x+sog.y+sog,
                  sum_blk = blk.x+blk.y+blk,
                  sum_hit = hit.x+hit.y+hit,       
                  sum_pim = pim.x+pim.y+pim,
                  sum_fow = fow.x+fow.y+fow,
                  sum_fol = fol.x+fol.y+fol,
                  sum_toi_gp = toi.gp.x+toi.gp.y+toi.gp,
                  sum_wtoi = tot.toi.x+tot.toi.y+tot.toi,
                  sum_lg_avg_toi = round(lg_avg_toi.x+lg_avg_toi.y+
                  lg_avg_toi, 2),
                  sum_lg_avg_g = lg_avg_g.x+lg_avg_g.y+lg_avg_g,
                  sum_lg_avg_a = lg_avg_a.x+lg_avg_a.y+lg_avg_a,
                  sum_lg_avg_pts = lg_avg_pts.x+lg_avg_pts.y+
                  lg_avg_pts,
                  sum_lg_avg_ppg = lg_avg_ppg.x+lg_avg_ppg.y+
                  lg_avg_ppg,
                  sum_lg_avg_ppa = lg_avg_ppa.x+lg_avg_ppa.y+
                  lg_avg_ppa,
                  sum_lg_avg_shg = lg_avg_shg.x+lg_avg_shg.y+
                  lg_avg_shg,
                  sum_lg_avg_sha = lg_avg_sha.x+lg_avg_sha.y+
                  lg_avg_sha,
                  sum_lg_avg_sog = lg_avg_sog.x+lg_avg_sog.y+
                  lg_avg_sog,
                  sum_lg_avg_blk = lg_avg_blk.x+lg_avg_blk.y+
                  lg_avg_blk,
                  sum_lg_avg_hit = lg_avg_hit.x+lg_avg_hit.y+
                  lg_avg_hit,
                  sum_lg_avg_pim = lg_avg_pim.x+lg_avg_pim.y+
                  lg_avg_pim,
                  sum_lg_avg_fow = lg_avg_fow.x+lg_avg_fow.y+
                  lg_avg_fow,
                  sum_lg_avg_fol = lg_avg_fol.x+lg_avg_fol.y+
                  lg_avg_fol)
              

#f & d are the amounts of toi that will regress the players production towards their positions league average. 
#Eg: A F with w_toi of 12500 will have their stat's regressed 9% towards league average while a F with 3000 w_toi will be regressed 29%
                  
f = 1250
d = 1750 

# to calc the non-age adjusted projections we have the following formula. If we were projecting goals it would be:
# [(summed g + lg avg g)/(sum toi + (1250 or 1750)]*GP*toi
# regressed goals is how many goals a lg average player would've scored in that players TOI
# This number is then multiplied by GP and toi

proj_plyr <- sum_plyr %>% transmute(
                player = player,
                age = age,
                pos= pos,
                gp = round(gp,0),
                proj_toi = proj_toi,
                proj_g =  round((((sum_lg_avg_g/sum_lg_avg_toi)*ifelse(pos == "F",f,d))+sum_g)/(ifelse(pos == "F",f,d)+sum_wtoi)*gp*proj_toi,2),
                proj_a =  round((((sum_lg_avg_a/sum_lg_avg_toi)*ifelse(pos == "F",f,d))+sum_a)/(ifelse(pos == "F",f,d)+sum_wtoi)*gp*proj_toi,2),
                proj_p =  round((((sum_lg_avg_pts/sum_lg_avg_toi)*ifelse(pos == "F",f,d))+sum_p)/(ifelse(pos == "F",f,d)+sum_wtoi)*gp*proj_toi,2),
                proj_ppa =  round((((sum_lg_avg_ppa/sum_lg_avg_toi)*ifelse(pos == "F",f,d))+sum_ppa)/(ifelse(pos == "F",f,d)+sum_wtoi)*gp*proj_toi,2),
                proj_ppg =  round((((sum_lg_avg_ppg/sum_lg_avg_toi)*ifelse(pos == "F",f,d))+sum_ppg)/(ifelse(pos == "F",f,d)+sum_wtoi)*gp*proj_toi,2),
                proj_ppp = proj_ppg+proj_ppa,
                proj_sha =  round((((sum_lg_avg_sha/sum_lg_avg_toi)*ifelse(pos == "F",f,d))+sum_sha)/(ifelse(pos == "F",f,d)+sum_wtoi)*gp*proj_toi,2),
                proj_shg =  round((((sum_lg_avg_shg/sum_lg_avg_toi)*ifelse(pos == "F",f,d))+sum_shg)/(ifelse(pos == "F",f,d)+sum_wtoi)*gp*proj_toi,2),
                proj_shp = proj_shg+proj_sha,
                proj_sog =  round((((sum_lg_avg_sog/sum_lg_avg_toi)*ifelse(pos == "F",f,d))+sum_sog)/(ifelse(pos == "F",f,d)+sum_wtoi)*gp*proj_toi,2),
                proj_hit =  round((((sum_lg_avg_hit/sum_lg_avg_toi)*ifelse(pos == "F",f,d))+sum_hit)/(ifelse(pos == "F",f,d)+sum_wtoi)*gp*proj_toi,2),
                proj_blk =  round((((sum_lg_avg_blk/sum_lg_avg_toi)*ifelse(pos == "F",f,d))+sum_blk)/(ifelse(pos == "F",f,d)+sum_wtoi)*gp*proj_toi,2),
                proj_pim =  round((((sum_lg_avg_pim/sum_lg_avg_toi)*ifelse(pos == "F",f,d))+sum_pim)/(ifelse(pos == "F",f,d)+sum_wtoi)*gp*proj_toi,2),
                proj_fow =  round((((sum_lg_avg_fow/sum_lg_avg_toi)*ifelse(pos == "F",f,d))+sum_fow)/(ifelse(pos == "F",f,d)+sum_wtoi)*gp*proj_toi,2),
                proj_fol =  round((((sum_lg_avg_fol/sum_lg_avg_toi)*ifelse(pos == "F",f,d))+sum_fol)/(ifelse(pos == "F",f,d)+sum_wtoi)*gp*proj_toi,2)
                )
                
# now we adjust the projections based on players age. Assumptions are that a player's aging is constant improvement/regression        
                
proj_stat_age <- proj_plyr %>% mutate_at(
                vars(starts_with("proj")), ~.*(ifelse(age <= 28, 
                (28 - age)*0.008, (28-age)*0.004)+1))
                
# this will produce a final cleaned up version of the projections                

final_proj <- proj_stat_age %>% transmute(
                player = player,
                age = age,
                pos= pos,
                gp = gp,
                toi = round(proj_toi,2),
                g =  round(proj_g,0),
                a =  round(proj_a,0),
                p =  g+a,
                ppg =  round(proj_ppg,0),
                ppa =  round(proj_ppa,0),
                ppp = ppa+ppg,
                shg =  round(proj_shg,0),
                sha =  round(proj_sha,0),
                shp = sha+shg,
                sog =  round(proj_sog,0),
                hit =  round(proj_hit,0),
                blk =  round(proj_blk,0),
                pim =  round(proj_pim,0),
                fow =  round(ifelse(pos == "F", proj_fow,0),0),
                fol = round(ifelse(pos == "F", proj_fol,0),0)
                ) %>% 
                # filter removes players that won't play reg minutes
                filter(toi >= 8)             

final_proj

}
```

# select which season you wish to project. Type in the year you would like. Eg: For the 2022-2023 season you would use 2023.

projected_season <- proj_season(2023)
